### 2018-08-16 manuscript/figures_and_tables.tex
use imputed data

\begin{figure}
\centering
%\includegraphics[scale=1]{../figures/figure-3}
\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship (in Model~5, Table~\ref{tab:t2}).}
\label{fig:f3}
\end{figure}

>>>>

\begin{figure}
\centering
%\includegraphics[scale=1]{../figures/figure-3}
\caption{Estimated probability of participants categorising a target as ``us'' versus ``not us'' as a function of the targets' group memberships (horizontal), the participants' group memberships (colour), and the reported amount of negative contact and outgroup friendship with the relevant groups         (in Model~5, Table~\ref{tab:t2}).}
\label{fig:f3}
\end{figure}
